Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-21 RR_manuscript/Draft_RR.Rmd

@@

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 2)

@@

# review ratings
review_mean <- msa_models %>% 
  summarise(mean_prating = mean(phon_rating, na.rm = TRUE),
            sd_prating = sd(phon_rating, na.rm = TRUE),
            mean_srating = mean(stat_rating, na.rm = TRUE),
            sd_srating = sd(stat_rating, na.rm = TRUE))
```

@@

\phantom{.}

```{r}
#| label: team-descriptives-table
#| echo: false
#| results: 'asis'
#| eval: true

# team_desc_df %>% 
#   mutate(Mean = glue::glue("{mean_size} ({sd_size})")) %>% 
#   select(Stage = stage, n = n_teams, Mean, Median = median_size) %>% 
#   knitr::kable(align = c("l", "r", "r", "r"), 
#                caption = "Caption test", 
#                label = "team-descriptives-table")

# Team descriptives
tbl_team_desc <- msa_models %>% 
  select(animal, years_from_phd, prior_belief, phon_rating, stat_rating, 
         all_rating) %>% 
  group_by(animal) %>% 
  summarize(across(years_from_phd:all_rating, mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals), sd = sd(vals)) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  mutate(desc = "team_desc", 
    metric = fct_relevel(metric, "years_from_phd"), 
   `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Metric = case_when(
      metric == "years_from_phd" ~ "Years since PhD", 
      metric == "stat_rating" ~ "Statistical ability", 
      metric == "prior_belief" ~ "Prior belief of $H_{1}$", 
      metric == "phon_rating" ~ "Phon rating", 
      metric == "all_rating" ~ "all rating"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd) %>% 
  add_row(label = " ", desc = "team_desc", Metric = " ", 
          Min. = NA, Max = NA, `Mean (SD)` = NA, avg = NA, sd = NA) %>% 
  mutate(across(-c("label", "desc", "Metric"), ~replace(., is.na(.), " ")))

# Model descriptives 
tbl_model_desc <- msa_models %>% 
  select(animal, n_predictors:n_random, n_models) %>% 
  group_by(animal) %>% 
  summarize(across(everything(), mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals), sd = sd(vals)) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  mutate(desc = "model_desc", 
    metric = fct_relevel(metric, "n_models"), 
    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Metric = case_when(
      metric == "n_coefficients" ~ "n. coefficients", 
      metric == "n_models" ~ "n. models", 
      metric == "n_predictors" ~ "n. predictors", 
      metric == "n_random" ~ "n. random effects", 
      metric == "n_random_int" ~ "n. random intercepts", 
      metric == "n_random_slo" ~ "n. random slopes", 
      metric == "n_random_smooth" ~ "n. random smooths",
      metric == "n_terms" ~ "n. terms"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd) %>% 
  mutate(across(-c("desc", "Metric"), as.character))

# Combine in single tibble (for printing in prose and table)
tbl_team_model_desc <- bind_rows(tbl_team_desc, tbl_model_desc) %>% 
  mutate(desc = case_when(
    Metric != "all rating" & desc == "team_desc" ~ " ", 
    Metric != "n. coefficients" & desc == "model_desc" ~ " ", 
    TRUE ~ desc), 
    desc = case_when(
      desc == "team_desc" ~ "Teams", 
      desc == "model_desc" ~ "Models", 
      TRUE ~ " "))

tbl_team_model_desc %>% 
  select(Descriptives = desc, Metric, Min., Max, `Mean (SD)`) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "l", "r", "r", "r"))

@@

Submitting teams consisted of an average of `r team_desc_list$Final$mean_size$val` individual analysts (SD = `r team_desc_list$Final$sd_size$val`).
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
Analysts had on average `r round(phd_mean[[1]],1)` years (SD = `r round(phd_mean[[2]],1)`) of experience after completing their PhD, ranging from `r round(phd_mean[[3]],1)` years, i.e. PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (SD = `r round(prior_mean[[2]],1)`).
We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r round(mean_analyses[[1]], 1)` models per team. 
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

@@

`r (round(window_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` percent of models obtained acoustic measures at the level of the segment (e.g. comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% from the word level (e.g. comparing the acoustic profile of *Banane* 'banana'), `r round(window_n[[3,1]],2) * 100`\% at the level of the phrase (e.g. the noun phrase including determiner and adjective, e.g. "the green banana"), `r round(window_n[[4,1]],2) * 100`\% from the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals. 
The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence. 
Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.

@@

The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects [e.g., @gelman2006data; @schielzeth2009conclusions]. 
`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication]. <!-- TR: Did we confirm this? -->
`r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models.

Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of `r nrow(unique_model_specs)` different model specifications.
When considering both acoustic and statistical analysis, we have found a grand total of `r nrow(unique_acou_stat)`, i.e. each submitted analysis was unique.

@@

Teams reviewed each others' acoustic and statistical analyses.
The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`).
The mean rating of the statistical analysis is `r round(review_mean[[3]],1)` (SD = `r round(review_mean[[4]],1)`).
For reference, as mentioned in the Methods section, a score of 75 was defined as "an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation", indicating that on average reviewers judged the provided analyses to be appropriate, although "imperfect".

>>>>

```{r}
#| label: helper-functions
# Round and format numbers to exactly N digits
specify_decimal <- function(x, k) {
  out <- trimws(format(round(x, k), nsmall = k))
  return(out)
}

# Print values from tibble for article
pull_from_tib <- function(df, col, row, val) {
  col <- enquo(col)
  row <- enquo(row)
  val <- enquo(val)
  val <- filter(df, !!col == !!row) %>% pull(!!val)
  return(val)
}
```

@@

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 1)

@@

# review ratings
# NOTE: Stef or Timo, this doesnt take into account repeated values per team
# so the denominator is inflated (alosa_atun has 16 models but the phon_rating 
# is the same for each so the mean is dividing by an inflated denominator)
# I suggest using the following: 
#  `pull_from_tib(tbl_team_desc, label, "team_desc_phon_rating", avg)`
#  `pull_from_tib(tbl_team_desc, label, "team_desc_phon_rating", sd)`

review_mean <- msa_models %>% 
  summarise(mean_prating = mean(phon_rating, na.rm = TRUE),
            sd_prating = sd(phon_rating, na.rm = TRUE),
            mean_srating = mean(stat_rating, na.rm = TRUE),
            sd_srating = sd(stat_rating, na.rm = TRUE))

#
# TABLE 1 PREP
#

# Team descriptives
tbl_team_desc <- msa_models %>% 
  select(animal, years_from_phd, prior_belief, phon_rating, stat_rating, 
         all_rating) %>% 
  group_by(animal) %>% 
  summarize(across(years_from_phd:all_rating, mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
            sd = sd(vals, na.rm = T)) %>% 
  add_row(.before = 1, 
    metric = "size", 
    min = team_desc_df %>% filter(stage == "Final") %>% pull(min), 
    max = team_desc_df %>% filter(stage == "Final") %>% pull(max), 
    avg = team_desc_df %>% filter(stage == "Final") %>% pull(mean_size), 
    sd =  team_desc_df %>% filter(stage == "Final") %>% pull(sd_size)) %>% 
  mutate(across(-metric, specify_decimal, k = 1)) %>% 
  mutate(desc = "team_desc", 
   `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Range = glue::glue("{min}--{max}"), 
    Metric = case_when(
      metric == "size" ~ "Team size", 
      metric == "years_from_phd" ~ "Years since PhD", 
      metric == "stat_rating" ~ "Self-report statistical ability", 
      metric == "prior_belief" ~ "Prior belief in $H_{1}$", 
      metric == "phon_rating" ~ "Acoustic analysis rating", 
      metric == "all_rating" ~ "Overall peer review rating"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range)

#
# TABLE 2 PREP
#

# Descriptives of categorical variables in acoustic analyses
tbl_categorical_desc <- msa_models_unique %>% 
  select(animal, outcome, temporal_window, typicality_operationalization, 
  framework, model) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "val") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  count(val) %>% 
  group_by(metric) %>% 
  mutate(prop = n / sum(n), perc = prop * 100, 
    Metric = case_when(
      metric == "temporal_window" ~ "Temporal window", 
      metric == "typicality_operationalization" ~ "Typicality operationalization", 
      TRUE ~ metric
    ), 
    Metric = str_to_sentence(Metric), 
    Type = case_when(
      val != "GAM" ~ str_to_sentence(val), 
      TRUE ~ val
    )) %>% 
  mutate(across(c("prop", "perc"), specify_decimal, k = 1)) %>% 
  unite(label, c("metric", "val")) %>% 
  mutate(label = str_replace_all(label, " ", "_"), 
         label = str_remove_all(label, "\\(|\\)"))

#
# TABLE 3 PREP
#

# Model descriptives 
tbl_model_desc <- msa_models %>% 
  select(animal, n_predictors:n_random, n_models) %>% 
  group_by(animal) %>% 
  summarize(across(everything(), mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
            sd = sd(vals, na.rm = T)) %>% 
  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
  mutate(across(c("avg", "sd"), specify_decimal, k = 1)) %>% 
  mutate(desc = "model_desc", 
    metric = fct_relevel(metric, "n_models"), 
    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Range = glue::glue("{min}--{max}"), 
    Metric = case_when(
      metric == "n_coefficients" ~ "n. coefficients", 
      metric == "n_models" ~ "n. models", 
      metric == "n_predictors" ~ "n. predictors", 
      metric == "n_random" ~ "n. random effects", 
      metric == "n_random_int" ~ "n. random intercepts", 
      metric == "n_random_slo" ~ "n. random slopes", 
      metric == "n_random_smooth" ~ "n. random smooths",
      metric == "n_terms" ~ "n. terms"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range) %>% 
  mutate(across(-c("desc", "Metric"), as.character))

@@

@@

Submitting teams consisted of an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` individual analysts (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`).
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e. PhD students (or younger) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years.
The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_team_desc, label, "model_desc_n_models", avg)` (SD: `r pull_from_tib(tbl_team_desc, label, "model_desc_n_models", sd)`) models per team. 
Table \@ref(tab:team-descriptives-table) provides a summary of the contributing teams and their analyses. 
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

<!-- Begin Table 1 --> 
\vspace{0.2in}
```{r}
#| label: team-descriptives-table
#| results: 'asis'
bind_rows(
  tbl_team_desc, 
  filter(tbl_model_desc, label == "model_desc_n_models")
  ) %>% 
  select(Metric, Range, `Mean (SD)`) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "c", "r"), 
    caption = "Descriptive statistics for teams included in the 
    meta-analysis (n = 30).",
    label = "team-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 11)
```
<!-- END: Table -->

@@

`r (round(window_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` percent of models obtained acoustic measures at the level of the segment (e.g. comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% from the word level (e.g. comparing the acoustic profile of *Banane* 'banana'), `r round(window_n[[3,1]],2) * 100`\% at the level of the phrase (e.g. the noun phrase including determiner and adjective, e.g. "the green banana"), `r round(window_n[[4,1]],2) * 100`\% from the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals. 
The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence. 
Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
Table \@ref(tab:categorical-descriptives-table) provides a summary of the acoustic analyses.

<!-- Begin Table 2 --> 
\vspace{0.2in}
```{r}
#| label: categorical-descriptives-table
#| results: 'asis'

tbl_categorical_desc %>% 
  select(Metric, Type, n, `\\%` = perc) %>% 
  group_by(Metric) %>% 
  arrange(desc(n), .by_group = T) %>% 
  ungroup() %>% 
  mutate(Metric = case_when(
    Type != "Frequentist" & Metric == "Framework" ~ " ", 
    Type != "Linear model" & Metric == "Model" ~ " ", 
    Type != "F0" & Metric == "Outcome" ~ " ", 
    Type != "Segment" & Metric == "Temporal window" ~ " ", 
    Type != "Categorical" & Metric == "Typicality operationalization" ~ " ", 
    TRUE ~ Metric)
    ) %>% 
  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 2) %>%
  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 6) %>%
  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 12) %>%
  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 18) %>%
  mutate(across(-c("Metric", "Type"), ~replace(., is.na(.), " "))) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "l", "r", "r"), 
    caption = "Descriptive statistics for model stuff.",
    label = "categorical-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 11)

```
<!-- END Table 2 -->

@@

The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects [e.g., @gelman2006data; @schielzeth2009conclusions]. 
`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication]. <!-- TR: Did we confirm this? -->
`r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models. 
Table \@ref(tab:stats-descriptives-table) provides a summary of the statistical analyses.

<!-- Found effect 
JVC: this code is ready to go, but not all the rows in the google sheet are 
filled out (approx. 40 missing)
--> 
```{r}
#| label: found-effect
#| echo: false

found_effect <- msa_models %>% 
  select(animal, model_n, found_effect) %>% 
  na.omit() %>% 
  mutate(effect = if_else(found_effect == "yes", 1, 0))

atleast_1_effect <- found_effect %>% 
  group_by(animal) %>% 
  summarize(total = sum(effect)) %>% 
  filter(total != 0)

# Overall N of analyses claiming an effect
n_effects <- sum(found_effect$effect)
# Percent of effects
perc_effects <- (n_effects / nrow(msa_models) * 100) %>% round(., 2)
# N of teams claiming an effect
n_atleast_1 <- nrow(atleast_1_effect)
# Percent of teams claiming an effect
perc_atleast_1 <- (n_atleast_1 / length(unique(msa_models$animal))) * 100
```

Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of `r nrow(unique_model_specs)` different model specifications.
When considering both acoustic and statistical analysis, we have found a grand total of `r nrow(unique_acou_stat)`, i.e. each submitted analysis was unique.
Of the submitted analyses, `r n_effects` claimed to have found a statistically reliable effect (`r perc_effects`%). 
`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) submitting analyses reported at least one found effect.

<!-- Begin Table 3 --> 
```{r}
#| label: stats-descriptives-table
#| results: 'asis'
tbl_model_desc %>% 
  select(Metric, Range, `Mean (SD)`) %>% 
  filter(Metric != "n. random smooths") %>% 
  mutate(Metric = str_remove_all(Metric, "n. "), 
         Metric = str_to_sentence(Metric)) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "c", "r"), 
    caption = "Descriptive statistics for statistical analyses included in the 
    meta-analysis (n = 30).",
    label = "stats-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 11)
```
<!-- END: Table -->

@@

Teams reviewed each others' acoustic and statistical analyses.
The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`, see Table \@ref(tab:team-descriptives-table)).
The mean rating of the statistical analysis is `r round(review_mean[[3]],1)` (SD = `r round(review_mean[[4]],1)`).
For reference, as mentioned in the Methods section, a score of 75 was defined as "an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation", indicating that on average reviewers judged the provided analyses to be appropriate, although "imperfect".
